Supplementary figures\nCapturing regeneration in models of forest dynamics

### 2023-04-14 manuscript/supplementaryRW.Rmd
updated references for landis model in the appendix

-   Scheller et al. 2007 -
    <https://doi.org/10.1016/j.ecolmodel.2006.10.00>
-   De Bruijn et al. 2014 -
    <https://doi.org/10.1016/j.ecolmodel.2014.05.004>
-   Petter et al. 2020 - <https://doi.org/10.1016/j.envsoft.2020.104844>
    (supplementary material)
-   User guide for PNET 4.1 online -
    <https://github.com/LANDIS-II-Foundation/Extension-PnET-Succession/blob/master/deploy/docs/LANDIS-II%20PnET-Succession%20v4.1%20User%20Guide.pdf>

>>>>

-   Scheller R.M. & Mladenoff D.J. (2004) A forest growth and biomass
    module for a landscape simulation model, LANDIS: design, validation,
    and application. Ecological Modelling 180:
    211--229. <https://doi.org/10.1016/j.ecolmodel.2004.01.022>
-   Scheller, R. M., Domingo J. B. , Sturtevant B. R. , Williams J. S. ,
    Rudy A. , Gustafson E. J. & Mladenoff D. J. (2007) Design,
    development, and application of LANDIS-II, a spatial landscape
    simulation model with flexible temporal and spatial resolution.
    Ecological Modelling 201(3-4): 409--419.
    <https://doi.org/10.1016/j.ecolmodel.2006.10.009>
-   de Bruijn A., Gustafson E.J. , Sturtevant B.R., Foster J.R., Miranda
    B.R., Lichti N.I. & Jacobs D.F. (2014) Toward more robust
    projections of forest landscape dynamics under novel environmental
    conditions: Embedding PnET within LANDIS-II. Ecological Modelling
    (287): 44--57 <https://doi.org/10.1016/j.ecolmodel.2014.05.004>
-   Petter G., Mairota P., Albrich K., Bebi P., Brůna J., Bugmann H.,
    Haffenden A., Scheller R.M., Schmatz D.R., Seidl R., Speich M.,
    Vacchiano G. & Lischke H. (2020) How robust are future projections
    of forest landscape dynamics? Insights from a systematic comparison
    of four forest landscape models. Environmental Modelling & Software
    134: 104844. <https://doi.org/10.1016/j.envsoft.2020.104844>
    (supplementary material)
-   Gustafson E.J., De Bruijn A.M.G., Pangle R.E., Limousin J.M.,
    Mcdowell N.G., Pockman W.T., Sturtevant B.R., Muss J.D. & Kubiske
    M.E. (2015) Integrating ecophysiology and forest landscape models to
    improve projections of drought effects under climate change. Global
    Change Biology 21: 843--856. <https://doi.org/10.1111/gcb.12713>\
